Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Cosmit.
Avoid footnote.

Started in 2009, \textit{scikit-learn} is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through thorough
code review.

Within the past few years, the project has proved valuable to an ever
increasing user base. Its popularity can be gaged from various indicators
such as hundreds of citations in scientific papers, successes in various
machine learning challenges (\emph{e.g.} kaggle), or significant
statistics\footnote{As of writing, 1309 stars and 667 forks of the
project on github, 300 mails per months on the user mailing list, 385
questions tagged \emph{scikit-learn} on {\tt stackoverflow}.} derived from
our repositories and mailing lists.

>>>>

Started in 2009, \textit{scikit-learn} is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through rigorous
code review.

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications of a previous paper
\citep{pedregosa2011}, successes in various machine learning challenges
(\emph{e.g.} kaggle), or significant statistics derived from our repositories
and mailing lists.  At the time of writing, the project is watched by 1309
people and forked 667 time on github, and the mailing-list receives 300 mails
per month.
